Results

### 2025-04-09 notebooks/00_index.qmd
feat: event plot

WI_H1_SWE	Proton_Wperp_nonlin	    Proton thermal speed perpendicular to the magnetic field direction [km/s].
WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].

@@

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"

mva_V_labels = ["V_L", "V_M", "V_N"]
```

```{julia}
psp_B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels)

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        _unitify(u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=n_ylabel
)

psp_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
    ];
    ylabel=Temp_ylabel
)

psp_V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels)

tvars_psp = [
    tnorm_combine ∘ psp_B,
    psp_n,
    psp_V,
    psp_temp
]
```

```{julia}
wind_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
    ];
    ylabel=n_ylabel
)

wind_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
    ];
    ylabel=Temp_ylabel
)

tvars_wind = [
    tnorm_combine ∘ SpeasyProduct("WI_H3-RTN_MFI/BRTN"; ylabel=B_ylabel, labels=B_labels),
    wind_n,
    tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    wind_temp
]
```

```{julia}
thm_temp = SPEDAS.DataSet(
    "Temperature",
    [
        "THB_L2_ESA/thb_peif_avgtempQ",
        tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label="Electron")
    ];
    ylabel=Temp_ylabel
)

tvars_themis = [
    tnorm_combine ∘ SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ"; ylabel=B_ylabel, labels=B_labels),
    ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"],
    SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ"; ylabel=V_ylabel, labels=V_labels),
    thm_temp,
]
```

@@

tau = Second(30)
psp_events = detect_variance(psp_B(tmin_psp, tmax_psp), tau)
```

```{julia}
function plot_candidate(event, ts)
    tplot(ts, event["tstart"], event["tstop"])
end

psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)

event = psp_events[2, :]
plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
```

### Plot

```{julia}
wind_proton_T3 = SPEDAS.DataSet("Thermal speed",
    ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]
)

tvars_wind2 = tvars_wind + [
    wind_proton_T3,
    "WI_ELM2_3DP/MAGT3"
]

tvars_themis2 = tvars_themis + [
    # SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
]
```

>>>>

WI_H1_SWE	Proton_Wperp_nonlin	    Proton thermal speed perpendicular to the magnetic field direction [km/s].
WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].
WI_PLSP_3DP	Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
WI_PM_3DP	Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP

@@

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set
using PSPAnisotropy
include("../src/psp_temp.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"

V_mva_labels = ["V_L", "V_M", "V_N"]
B_mva_labels = ["B_L", "B_M", "B_N"]
```

```{julia}
tvars_psp = [
    tnorm_combine ∘ PSP.B,
    PSP.n,
    PSP.V,
    PSP.T
]
```

```{julia}
tvars_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    tsubtract ∘ Wind.V,
    wind_temp
]
```

```{julia}
tvars_themis = [
    tnorm_combine ∘ THEMIS.B,
    THEMIS.n,
    THEMIS.V_GSE,
    THEMIS.T,
]
```

@@

tau = Second(30)
psp_events = detect_variance(PSP.B(tmin_psp, tmax_psp), tau)
wind_events = detect_variance(Wind.B(tmin_wind, tmax_wind), tau)
thm_events = detect_variance(THEMIS.B_FGL_GSE(tmin_wind, tmax_wind), tau)
```

```{julia}
psp_B_mva = set(mva ∘ PSP.B; name="mva_B", labels=B_mva_labels)
psp_V_mva = Product((PSP.V, PSP.B), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
psp_pTemp_ani = Product(read_proton_temperature(), tview; labels=["Proton (parallel)", "Proton (perpendicular)"])
psp_Temp_ani = [psp_eTemp_ani, psp_pTemp_ani]
psp_mva_all = [psp_B_mva, psp_V_mva, psp_Temp_ani]

wind_B_mva = set(mva ∘ Wind.B; name="mva_B", labels=B_mva_labels)
wind_V_mva = Product((Wind.V_GSE, Wind.B_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
wind_mva_all = [wind_B_mva, wind_V_mva, Wind.Temp_ani]

thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=B_mva_labels)
thm_V_mva = Product((THEMIS.V_GSE, THEMIS.B_FGL_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
thm_mva_all = [thm_B_mva, thm_V_mva, THEMIS.T_ani]
```

```{julia}
using DataFrames

@kwdef struct Event
    start
    stop
    metadata = Dict()
end

Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict())

(P::AbstractProduct)(e::Event) = P(e.start, e.stop)
```

```{julia}
function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
    tplot(f, ts, event.tstart - toffset, event.tstop + toffset; kwargs...)
end

let link_xaxes = false
    tvars_wind = [
        tnorm_combine ∘ Wind.B,
        Wind.n,
        Wind.V_GSE,
        Wind.temp,
        wind_B_mva,
        wind_V_mva,
        Wind.Temp_ani
    ]

    tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]

    f = Figure(; size=(1200, 800))
    plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
    wind_plots = plot_candidate(f[1, 2], Event(wind_events, 3), tvars_wind, Minute(1); link_xaxes)
    themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
    # hideydecorations!(wind_plots)
    # hideydecorations!(themis_plots)
    f
end
```
